ohbm_results

### 2023-12-05 paper_figs.Rmd
sex bias analyses

ggplot(z_diffs) +
  geom_jitter(aes(x=sex, y=diff_WMV.z, color=WMV.z), width = 0.2, height = 0, alpha=0.2) +
  #geom_smooth(method="lm") +
  facet_grid(sim.site~dataset) +
  #paletteer::scale_color_paletteer_c("grDevices::Cork") +
  theme_bw()

ggplot(z_diffs, aes(x=dataset, y=diff_WMV.z, color=sex)) +
  geom_boxplot() +
  theme_bw() +
  stat_compare_means(aes(group = sex))
```

@@

ggplot(cent_diffs, aes(x=WMV, y=diff_WMV, color=sex)) +
  geom_point(alpha=0.1, aes(shape=sim.site)) +
  geom_smooth(method="lm") +
  facet_wrap(~dataset)
```
```{r}
ggplot(z_diffs, aes(x=dataset, y=diff_WMV.z, color=sex)) +
  geom_boxplot() +
  theme_bw() +
  stat_compare_means(aes(group = sex))
```

>>>>

ggplot(z_diffs) +
  geom_jitter(aes(x=sex, y=diff_WMV.z, color=WMV.z), width = 0.2, height = 0, alpha=0.2) +
  #geom_smooth(method="lm") +
  facet_grid(sim.site~dataset) +
  paletteer::scale_color_paletteer_c("grDevices::Cork") +
  theme_bw()

ggplot(z_diffs, aes(x=dataset, y=diff_WMV.z, color=sex)) +
  geom_boxplot() +
  theme_bw() +
  stat_compare_means(aes(group = sex))

ggplot(z_diffs, aes(x=dataset, y=diff_WMV.z, color=sim.site)) +
  geom_boxplot() +
  theme_bw() +
  stat_compare_means(aes(group = sim.site, label = paste0("p = ", after_stat(p.format))))
```

```{r}
ggplot(z_diffs) +
  geom_boxplot(aes(y=diff_WMV.z, x=sim.site, color=sex)) +
  #geom_jitter(aes(y=diff_WMV.z, x=sim.site, color=sex), alpha=0.3) +
  #geom_smooth(method="lm", aes(linetype=sim.site)) +
  facet_wrap(~dataset)
```

@@

ggplot(cent_diffs, aes(x=WMV, y=diff_WMV, color=sex)) +
  geom_point(alpha=0.1, aes(shape=sim.site)) +
  geom_smooth(method="lm") +
  facet_wrap(~dataset)
```
```{r}
ggplot(cent_diffs, aes(x=dataset, y=diff_WMV, color=sex)) +
  geom_boxplot() +
  theme_bw() +
  stat_compare_means(aes(group = sex))
```
